Dynamic Topic Modeling for Voice Dialogues

### 2024-05-13 paper/main.tex
add lib + change picture
add seg

\section{Improving Utterance-Pair Coherence Scoring}

@@

The first optional stage is the Speaker Diarization. 
For audio dialogues, text is extracted from the audio track before topic segmentation. 
For this stage we use:
\begin{itemize}
    \item OpenAI Whisper \\
    Link to model: \href{https://huggingface.co/openai/whisper-large-v3}{whisper-large-v3};
    \item pyannote SpeakerDiarization library \\
    Link to model: \href{https://huggingface.co/pyannote/speaker-diarization-3.0}{speaker-diarization-3.0};
\end{itemize}

@@

>>>>

\section{Improving Utterance-Pair Coherence Scoring}
\label{seg}

@@

The first optional stage is the Speaker Diarization. 
For audio dialogues, text is extracted from the audio track before topic segmentation. 
For this stage we use:
\begin{itemize}
    \item OpenAI Whisper \\
    Link to model: \href{https://huggingface.co/openai/whisper-large-v3}{whisper-large-v3};
    \item pyannote - speaker diarization library \cite{pyannote:2023} \\
    Link to model: \href{https://github.com/pyannote/pyannote-audio}{[pyannote]};
\end{itemize}

@@

The algorithm \ref{seg} will be used to dialogues segmentation. 
The implementation of the algorithm will be taken from the \href{https://github.com/lxing532/Dialogue-Topic-Segmenter}{official github repository}. 
Part of the code with the model inference will be adapted to the pipeline.
